True Lies

### 2019-05-30 GSV-comment-brief.Rmd
changes for revision 2:  - change Liars to lambda  - remove experiment suggestion

Results in Table
\ref{tab:coverage-allmethods} show that both frequentist and  Bayesian methods mostly achieve the nominal
confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
exception is the frequentist 99% confidence interval, which is too narrow.

@@

Lastly, here is an idea for a simple experimental design to avoid these statistical shenanigans. Ask a
group of *N* experimental subjects, not to flip a coin, but to draw a black or white ball, without
replacement, from an urn containing *N* balls, of which *T* are white. Pay them if they report a
white ball. (Obviously, don't let them observe previous draws.) You will then know -- not estimate --
that the proportion of lies told is $(R - T)/(N - T)$, and this will also be the proportion of
liars, in a sample of exactly $N - T$ subjects. You can compare different samples, or test for no
lying, with a straightforward chi-squared test. The experimenter now knows exactly the
number of liars, and subjects will understand this, which may change the incentives to lie
 (maybe subjects don't like giving the experimenter certain knowledge that somebody lied).
But it simplifies the statistics. This design allows the experimenter to learn the exact proportion 
of lies, and the lying liars who tell them.

@@

Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and $\lambda$,
for *N* of 10 and 50. The Bayesian method is best for all values of *Liars* up to 80%.

>>>>

Results in Table
\ref{tab:coverage-allmethods} show that both frequentist and  Bayesian methods mostly achieve the nominal
confidence level, with more than 90/95/99% of intervals containing the true value of $\lambda$. The
exception is the frequentist 99% confidence interval, which is too narrow.

@@

@@

Figure \ref{fig:errors-by-true-prop} shows mean squared error by estimation method and $\lambda$,
for *N* of 10 and 50. The Bayesian method is best for all values of $\lambda$ up to 80%.
